### 2021-10-13 paper/paper.tex
update figures

\begin{figure*}
        \centering
        \begin{subfigure}[b]{0.45\textwidth}
            \centering
            \includegraphics[width=\textwidth]{fig/images/accuracy_vs_n.png}
            % \caption[Accuracy versus number of data points($d=64, \sigma=1.0, k=10$)]%
            {{\small Accuracy versus number of data points($d=64, \sigma=1.0, k=10$)}}  
            \label{subfig.1}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{fig/images/accuracy_vs_d.png}
            % \caption[Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, k=10$)]%
            {{\small Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, k=10$)}}
            \label{subfig.2}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.45\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{fig/images/accuracy_vs_sigma.png}
            % \caption[Accuracy versus randomness($n=100, d=64, k=10$)]%
            {{\small Accuracy versus randomness($n=100, d=64, k=10$)}}
            \label{subfig.3}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{fig/images/accuracy_vs_class.png}
            % \caption[Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)]%
            {{\small Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)}}   
            \label{subfig.4}
        \end{subfigure}
        % \caption[ Figures of Synthetic Data Experiment ]
        % {{\small Figures of Synthetic Data Experiment}}
        \label{fig.1}
    \end{figure*}

\begin{figure*}
        \centering
        \begin{subfigure}[b]{0.45\textwidth}
            \centering
            \includegraphics[width=\textwidth]{fig/new_img/accuracy_vs_base.png}
            {{\small Accuracy versus base of tree($n=1000, d=10, \sigma=1.0, k=100$)}}
            \label{subfig.1}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.45\textwidth}  
            \centering 
            \includegraphics[width=\textwidth]{fig/new_img/height_vs_base.png}
            {{\small Height versus base of tree($n=1000, d=10, \sigma=1.0, k=100$)}}   
            \label{subfig.2}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.45\textwidth}   
            \centering 
            \includegraphics[width=\textwidth]{fig/new_img/loss_vs_structure.png}
            % \caption[Accuracy versus randomness($n=100, d=64, k=10$)]%
            {{\small Accuracy versus tree structure($n=1000, d=64, \sigma=1.0, k=100$)}}  
            \label{subfig.3}
        \end{subfigure}
        \hfill
        % \begin{subfigure}[b]{0.45\textwidth}   
        %     \centering 
        %     \includegraphics[width=\textwidth]{fig/new_img/loss_vs_base.png}
        %     % \caption[Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)]%
        %     {{\small Loss versus base of cover tree($n=1000, d=10, \sigma=1.0, k=100$)}}    
        %     \label{subfig.4}
        % \end{subfigure}
        % \caption[ Figures of Synthetic Data Experiment ]
        % {{\small Figures of Synthetic Data Experiment}} 
        \label{fig.2}
    \end{figure*}

>>>>

\begin{figure}[h]
\vspace{.3in}
\includegraphics[width=\linewidth]{fig/images/accuracy_vs_n.png}
\vspace{.3in}
\caption{\small Accuracy versus number of data points($d=64, \sigma=1.0, k=10$)}
\label{accuracy_vs_n}
\end{figure}

\begin{figure}[h]
\vspace{.3in}
\includegraphics[width=\linewidth]{fig/images/accuracy_vs_d.png}
\vspace{.3in}
\caption{\small Accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, k=10$)}
\label{accuracy_vs_d}
\end{figure}

\begin{figure}[h]
\vspace{.3in}
\includegraphics[width=\linewidth]{fig/images/accuracy_vs_sigma.png}
\vspace{.3in}
\caption{\small Accuracy versus randomness($n=100, d=64, k=10$)}
\label{accuracy_vs_sigma}
\end{figure}

\begin{figure}[h]
\vspace{.3in}
\includegraphics[width=\linewidth]{fig/images/accuracy_vs_class.png}
\vspace{.3in}
\caption{\small Accuracy versus number of classes($n=100, d=64, \sigma=1.0$)}
\label{accuracy_vs_class}
\end{figure}

\begin{figure}[h]
\vspace{.3in}
\includegraphics[width=\linewidth]{fig/new_img/accuracy_vs_base.png}
\vspace{.3in}
\caption{\small Accuracy versus base of tree($n=1000, d=10, \sigma=1.0, k=100$)}
\label{accuracy_vs_base}
\end{figure}

\begin{figure}[h]
\vspace{.3in}
\includegraphics[width=\linewidth]{fig/new_img/height_vs_base.png}
\vspace{.3in}
\caption{\small Height versus base of tree($n=1000, d=10, \sigma=1.0, k=100$)}
\label{height_vs_base}
\end{figure}

\begin{figure}[h]
\vspace{.3in}
\includegraphics[width=\linewidth]{fig/new_img/loss_vs_structure.png}
\vspace{.3in}
\caption{\small Accuracy versus tree structure($n=1000, d=64, \sigma=1.0, k=100$)}
\label{accuracy_vs_structure}
\end{figure}
